Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-20 PaperVictor.tex
Corregi errores ortograficos

\notaL{Creo que no se ha explicado el proceso de diseño. No sé para
  qué damos tanto detalle sobre cómo se calculó, dado que todo está en
  la referencia.}

@@

Another class of techniques for designing good reflectors across a wide spectral range
is to stack sub-mirrors tuned to different wavelengths chosen with
different criteria. 
\notaV{I rewrote this "For example, Agarwal et al. 
	\cite{Agarwal2003} proposed to stack sub-mirrors as follows: 
	tune the first sub-mirror to certain wavelength $\lambda_{1}$. 
	Tune subsequent submirrors $j$ to wavelengths $\lambda_j$, 
	chosen so that $\lambda_{j+1} + \lambda_{j}=2+j$."} 
For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic 
structure in which she stacked 54 sub-mirrors as follows: the 
first sub-mirror consisted of 2.5 periods and tuned it to 
$\lambda_{1}=700$ nm; the following sub-mirrors were tuned to the 
wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1} 
+ \lambda_{j}=2+j$ with 4 periods for each of the following 
periods.
\notaL{This cannot be correct. Please check}. Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
developed a method that combines three stochastic optimization algorithms together with
a  narrow space search methodology to obtain a customized and optimized
PC configuration.

We recall that for a periodic structure, the propagation of
electromagnetic waves is described by the dispersion relation
\begin{equation}
	 \cos (KD) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
\end{equation}
where $K$ is Bloch's vector, $\bm M$ the transfer matrix of a single
period of thickness $D$ \cite{Mochan1987, Mochan1988,
  Perez2018}. \notaL{Tr was already defined and the reference to the
  equation is wrong:  denotes the trace
and $M$ is the matrix given by Eq. \ref{MsBloch}}. \notaV{Entendido, gracias} Thus,
whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
electromagnetic energy cannot propagate in the periodic system and we
expect a high reflectance for a finite system made of a finite number
of periods. This suggests the following design. We stack submirrors
each made of a few periods of a periodic system such that its photonic band gap
(PBG) overlaps the PBG of the previous and that of the next
submirror. The number of periods of each sub-mirror is an
important parameter. If it is too small, the sub-mirror would be
partially transparent within the PBG. If it is too large, the
resulting structure would be too thick. We followed two design
strategies: In the first, we considered sub-mirrors each with the same
number of periods. In the second, a different number of periods was
assigned to each submirrors with a PBG center within different
spectral regions: we used a single period for
$\lambda_{D}<500$ nm, two periods for $500 <\lambda_ {D} < 650$ nm
and three periods for $650<\lambda_ {D}<800$ nm.  and for
$\lambda_{D} \geq 800$ nm, the number of periods was variable.
\notaL{No se entiende. Los números uno, dos, tres ¿se sacaron de la manga? ¿se optimizaron? Para <800, ¿de dónde se sacó el número de periodos?}
\notaV{Los números de periodos uno, dos, tres, los eleg\'{i} para 
	que la estructura tenga pocos periodos en la region visible. 
	Adem\'{a}s, del c\'{a}lculo de las Trazas y reflectancias de 
	los subespejos individuales sintonizados de 1000 a 2500 nm, 
	tambi\'{e}n tienen una regi\'{o}n de propagaci\'{o}n prohibida 
	en el intervalo de 400 a 900 y la reflectancia es mayor al 
	80\%. Esto se puede observar en la Fig. SITrazasyRefSE.pdf}
In both designs, the optimal overlap of two consecutive PBGs was obtained that maximized reflectance.
\notaL{No quisiste decir average reflectance $\braket{R}$?. Si sí, en qué rango promediaste?} \notaV{Si, se promedi\'{o} en el siguiente rango}
Reflectance spectra were calculated for
$400\text{nm}\le \lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$.

Table \ref{tab:table2} shows the number of periods of each sub-mirror ($p$),
\notaL{Está difícil esta notación. ¿De dónde vienen la s y
  la e. $Np_{se}$ parece el producto de $N$ con $p_{se}$. ¿De dónde la p?} \notaV{Lo cambi\'{o} por $p$ de periods y $N$ de N\'{u}mero total de periodos}
the total number of stacked sub mirrors ($N_{se}$)
\notaL{El encabezado de la tabla está mal} \notaV{Corregido}, the
thickness of the structure, the optimal overlap of two consecutive
PBGs and the average reflectance. The first block corresponds to
sub-mirrors with a constant number of periods, while the second block
corresponds to sub-mirrors with a variable number of periods according
to the design wavelength. \notaL{No entiendo nada: qué dejaste 
	fijo y qué permitiste variar para optimizar en cada bloque de la tabla?}
\notaV{En el primer bloque \'{u}nicamente se optimiz\'{o} el traslape de dos PBGs consecutivos. En el segundo bloque, se optimizaron el n\'{u}mero de periodos (de 4 a 10 periodos) de los subespejos sintonizados a $\lambda_{D} \geq 800$ nm y el traslape de dos PBGs consecutivas.} 
\begin{table}[htbp]
  \begin{center}
    \caption{Parameters that maximize $\braket{R}$ for  stacked sub-mirrors.}
    \label{tab:table2}
    \begin{tabular}{|c|c|c|c|c|}
      \hline % <-- Toprule here
      \textbf{$p$}&{\textbf{$N$}} &\textbf{Thickness}&\textbf{Overlap}&$\braket{R}$\\
			&&($\mu$m)& \textbf{PBG $\%$}&$\%$\\
      \hline
      1&98&43.2&95&91.0\\
      3&31&42.5&81&91.8\\
      5&17&41.9&68&92.0\\
      \hline
      4&25&38.7&74&92.3\\\textcolor{red}{6}&\textcolor{red}{18}&\textcolor{red}{41.5} &\textcolor{red}{78} & \textcolor{red}{95.35}\\
      10&13&45.4&56&95.34\\
      \hline
    \end{tabular}
  \end{center}
\end{table}

@@

Fig. \ref{Fig3}(a) reveals a quasi omnidirectional
mirror in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
$60^\circ$. It is also observed that at incidence angles $\theta
>70^\circ$ and long
wavelengths the reflectance decreases and has oscillations, which are attributed to the
greater penetration of the electromagnetic field within the structure, as shown by
Puente-D\'{\i}az, et al. \cite{Puente2020}. In Fig. \ref{Fig3}(b) we compare the
calculated and measured reflectance for the structure $S_3$ at several angles of
incidence. Although, the quasi omnidirectional wavelength range of the synthesized
structure is slightly smaller than the calculated one, from 950 to 2750 nm, the measured
PBG is almost twice as wide as a recently reported PS chirped
structure \cite{Chavez2020}. \notaL{Por qué comparamos con ésta? 
	¿Era la mejor que había? Habría que decirlo}
\notaV{S\'{i}, es la estructura, a base de SP, que tiene el mayor ancho OD}

>>>>

\notaL{Creo que no se ha explicado el proceso de diseño. No sé para
  qué damos tanto detalle sobre cómo se calculó, dado que todo está en la referencia.}
\notaV{El proceso de diseño se explica en la secci\'{o}n de discusi\'{o}n y \}resultados}

@@

Another class of techniques for designing good reflectors across a wide spectral range
is to stack sub-mirrors tuned to different wavelengths chosen with
different criteria. 
\notaV{I rewrote this "For example, Agarwal et al. 
	\cite{Agarwal2003} proposed to stack sub-mirrors as follows: 
	tune the first sub-mirror to certain wavelength $\lambda_{1}$. 
	Tune subsequent submirrors $j$ to wavelengths $\lambda_j$, 
	chosen so that $\lambda_{j+1} - \lambda_{j}=2+j$."} 
For example, Agarwal et al. \cite{Agarwal2003} proposed a photonic 
structure in which she stacked 54 sub-mirrors as follows: the 
first sub-mirror consisted of 2.5 periods and tuned it to 
$\lambda_{1}=700$ nm; the following sub-mirrors were tuned to the 
wavelengths $\lambda_{j}$ according to the sequence $\lambda_{j+1} 
- \lambda_{j}=2+j$ (with its suitable units) with 4 periods for 
each of the following periods. 
\notaL{This cannot be correct. Please check}. Furthermore, Estrada-Wiese et al. \cite{DelRio2018}
developed a method that combines three stochastic optimization algorithms together with
a  narrow space search methodology to obtain a customized and optimized
PC configuration.

We recall that for a periodic structure, the propagation of
electromagnetic waves is described by the dispersion relation
\begin{equation}
	 \cos (KD) = \frac{1}{2} \text{Tr} \bm M,   \label{Dispersion}
\end{equation}
where $K$ is Bloch's vector, $\bm M$ the transfer matrix of a single
period of thickness $D$ \cite{Mochan1987, Mochan1988,
  Perez2018}. \notaL{Tr was already defined and the reference to the
  equation is wrong:  denotes the trace
and $M$ is the matrix given by Eq. \ref{MsBloch}}. \notaV{Entendido, gracias} Thus,
whenever $\left\vert\text {Tr} \left(M \right) \right\vert>2$
electromagnetic energy cannot propagate in the periodic system and we
expect a high reflectance for a finite system made of a finite number
of periods. This suggests the following design. We stack submirrors
each made of a few periods of a periodic system such that its photonic band gap
(PBG) overlaps the PBG of the previous and that of the next
submirror. The number of periods of each sub-mirror is an
important parameter. If it is too small, the sub-mirror would be
partially transparent within the PBG. If it is too large, the
resulting structure would be too thick. We followed two design
strategies: In the first, we considered sub-mirrors each with the same
number of periods. In the second, a different number of periods was
assigned to each submirrors with a PBG center within different
spectral regions: we used a single period for
$\lambda_{D}<500$ nm, two periods for $500 <\lambda_ {D} < 650$ nm
and three periods for $650<\lambda_ {D}<800$ nm.  and for
$\lambda_{D} \geq 800$ nm, the number of periods was variable.
\notaL{No se entiende. Los números uno, dos, tres ¿se sacaron de la manga? ¿se optimizaron? Para <800, ¿de dónde se sacó el número de periodos?}
\notaV{Los números de periodos uno, dos, tres, los eleg\'{i} para 
	que la estructura tenga pocos periodos en la region visible. 
	Adem\'{a}s, del c\'{a}lculo de las Trazas y reflectancias de 
	los subespejos individuales sintonizados de 1000 a 2500 nm, 
	tambi\'{e}n tienen una regi\'{o}n de propagaci\'{o}n prohibida 
	en el intervalo de 400 a 900 y la reflectancia es mayor al 
	80\%. Esto se puede observar en la Fig. SITrazasyRefSE.pdf} 
\notaV{Tambi\'{e}n fue a prueba y error}
In both designs, the optimal overlap of two consecutive PBGs was 
obtained that maximizes the average reflectance $\braket{R}$.
\notaL{No quisiste decir average reflectance $\braket{R}$?. Si sí, en qué rango promediaste?} \notaV{Si, se promedi\'{o} en el siguiente rango}
Reflectance spectra were calculated for
$400\text{nm}\le \lambda\le 3000\text{nm}$ and for $0^\circ\le\theta\le90^\circ$.

Table \ref{tab:table2} shows the number of periods of each sub-mirror ($p$),
\notaL{Está difícil esta notación. ¿De dónde vienen la s y
  la e. $Np_{se}$ parece el producto de $N$ con $p_{se}$. ¿De dónde la p?} \notaV{Lo cambi\'{o} por $p$ de periods y $N$ de N\'{u}mero total de periodos}
the total number of stacked sub mirrors ($N$)
\notaL{El encabezado de la tabla está mal} \notaV{Corregido}, the
thickness of the structure, the optimal overlap of two consecutive
PBGs and the average reflectance. The first block corresponds to
sub-mirrors with a constant number of periods, while the second block
corresponds to sub-mirrors with a variable number of periods according
to the design wavelength. \notaL{No entiendo nada: qué dejaste 
	fijo y qué permitiste variar para optimizar en cada bloque de la tabla?}
\notaV{En el primer bloque \'{u}nicamente se optimiz\'{o} el traslape de dos PBGs consecutivos. En el segundo bloque, se optimizaron el n\'{u}mero de periodos (de 4 a 10 periodos) de los subespejos sintonizados a $\lambda_{D} \geq 800$ nm y el traslape de dos PBGs consecutivas.} 
\begin{table}[htbp]
  \begin{center}
    \caption{Parameters that maximize $\braket{R}$ for  stacked sub-mirrors.}
    \label{tab:table2}
    \begin{tabular}{|c|c|c|c|c|}
      \hline % <-- Toprule here
      \textbf{$p$}&{\textbf{$N$}} &\textbf{Thickness}&\textbf{Overlap}&$\braket{R}$\\
			&&($\mu$m)& \textbf{PBG $\%$}&$\%$\\
      \hline
      1&98&43.2&95&91.0\\
      3&31&42.5&81&91.8\\
      5&17&41.9&68&92.0\\
      \hline
      4&25&38.7&74&92.3\\\textcolor{red}{6}&\textcolor{red}{18}&\textcolor{red}{41.5} &\textcolor{red}{78} & \textcolor{red}{95.35}\\
      10&13&45.4&56&95.34\\
      \hline
    \end{tabular}
  \end{center}
\end{table}

@@

Fig. \ref{Fig3}(a) reveals a quasi omnidirectional
mirror in the range from 950 to 2900 nm, with an angular range between $0^\circ$ and
$60^\circ$. It is also observed that at incidence angles $\theta
>70^\circ$ and long
wavelengths the reflectance decreases and has oscillations, which are attributed to the
greater penetration of the electromagnetic field within the structure, as shown by
Puente-D\'{\i}az, et al. \cite{Puente2020}. In Fig. \ref{Fig3}(b) we compare the
calculated and measured reflectance for the structure $S_3$ at several angles of
incidence. Although, the quasi omnidirectional wavelength range of 
the synthesized structure is slightly smaller than the calculated 
one, from 950 to 2750 nm, the measured PBG is almost twice as wide 
as a recently reported PS chirped structure \cite{Chavez2020}, his 
structure has the largest reported OD width.. 
\notaL{Por qué comparamos con ésta? 
	¿Era la mejor que había? Habría que decirlo}
\notaV{S\'{i}, es la estructura, a base de SP, que tiene el mayor ancho OD}
